Renewal and stability in populations structured by remaining years of life

### 2014-08-27 ThanoRepro/ThanoRepro.tex
abstract

\begin{abstract}
Aggregate data classified by chronological age can be transformed into data
classified by remaining years of life (thanatological age). A model for population renewal and
the corresponding projection matrix are presented for populations structured by
thanatological age. Period results are derived using all available data from the
HMD and HFD. We compare the intrinsic growth rate, $r$, as derived from the
classic Lotka equation versus that derived on the basis of thanatological age.
We also compare some transient indicators between the two
models. Empirical results suggest that $r$ from the thanatological model tends to be less erratic than
Lotka's $r$, and the trajectory to stability tends to be faster with less
oscillation.
\end{abstract}

>>>>

\begin{abstract}
A unisex model of population renewal for populations structured by
thanatological age is presented in both continuous and discrete form. Various
stable and transient properties populations are compared and related when viewed
by chronological versus thanatological age. Results from the two age perspectives are conformable if the starting
population is stable, but are otherwise divergent.
\end{abstract}
